\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\usepackage{hyperref}
\usepackage{amsmath}

\title{Corporate and Government Crimes Against Open Source}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This document details the unethical practices of major corporations and governments—including Nintendo, Sony, Apple, Microsoft, Google, Meta, Amazon, Oracle, Nvidia, Tesla, Broadcom, IBM, the U.S. Government, and the Trump Administration—against the open-source community. It highlights their exploitation of free software, suppression of independent development, and legal attacks against modders, developers, and right-to-repair movements. Additionally, it outlines targeted countermeasures that the open-source community can use to force these entities into compliance.
\end{abstract}

\section{Introduction}
The open-source community thrives on collaboration, transparency, and shared progress. However, many corporations and governments have taken advantage of free software while giving nothing back, or worse, actively suppressing the freedoms of users and developers. This document catalogs their offenses and outlines strategies to hold them accountable.

\newpage
\section{Crimes of Corporations Against Open Source}

\subsection{1. Nintendo}
\textbf{Crimes:}
\begin{itemize}
    \item Aggressive legal action against homebrew developers and open-source emulators.
    \item Suing and shutting down open-source projects such as Yuzu and Dolphin.
    \item Using open-source software (like FreeBSD) while refusing to contribute back.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support open-source alternatives and independent developers.
    \item Expose Nintendo’s hypocrisy regarding FreeBSD usage.
\end{itemize}

\subsection{2. Sony}
\textbf{Crimes:}
\begin{itemize}
    \item PlayStation OS (OrbisOS) is based on FreeBSD, but Sony refuses to open-source its modifications.
    \item Locks down hardware to prevent custom firmware and homebrew development.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Demand compliance with FreeBSD’s licensing terms.
    \item Promote open-source gaming platforms as alternatives.
\end{itemize}

\subsection{3. Apple}
\textbf{Crimes:}
\begin{itemize}
    \item Exploits open-source projects like LLVM, WebKit, and BSD but locks down its ecosystem.
    \item Uses legal threats against open-source repair communities.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support Right-to-Repair movements.
    \item Promote Linux-based alternatives to macOS.
\end{itemize}

\subsection{4. Microsoft}
\textbf{Crimes:}
\begin{itemize}
    \item Acquired GitHub and used it to push corporate control over open-source development.
    \item Attempted to replace open standards with proprietary formats.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Promote self-hosted Git alternatives like Gitea.
    \item Encourage the use of open formats over Microsoft Office.
\end{itemize}

\subsection{5. Google}
\textbf{Crimes:}
\begin{itemize}
    \item Abandons open-source projects (Google Code, Android Open Source Project).
    \item Limits third-party access to Android system-level modifications.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support alternatives like GrapheneOS.
    \item Pressure Google to maintain open-source commitments.
\end{itemize}

\subsection{6. Meta (Facebook)}
\textbf{Crimes:}
\begin{itemize}
    \item Uses open-source machine learning tools but contributes minimally.
    \item Implements DRM that restricts software freedom.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support decentralized social media alternatives.
    \item Promote open-source AI initiatives.
\end{itemize}

\subsection{7. Oracle}
\textbf{Crimes:}
\begin{itemize}
    \item Sued Google over Java APIs, threatening software interoperability.
    \item Exploits open-source databases while restricting usage of its own tools.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Avoid Oracle products.
    \item Support open-source database projects like PostgreSQL.
\end{itemize}

\newpage
\section{Crimes of the U.S. Government Against Open Source}

\subsection{1. Suppression of Open-Source Cryptography}
\textbf{Crimes:}
\begin{itemize}
    \item Restricted export of open-source encryption tools.
    \item NSA sabotaged cryptographic standards (Dual\_EC\_DRBG scandal).
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support privacy-focused open-source projects.
\end{itemize}

\subsection{2. Right-to-Repair Suppression}
\textbf{Crimes:}
\begin{itemize}
    \item DMCA prevents independent hardware repair.
    \item Pressure from corporations like Apple and John Deere.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support Right-to-Repair legislation.
\end{itemize}

\subsection{3. Government Surveillance Using Open-Source Software}
\textbf{Crimes:}
\begin{itemize}
    \item NSA and FBI use open-source big data software for mass surveillance.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Fund privacy-respecting open-source alternatives.
\end{itemize}

\newpage
\section{Crimes of the Trump Administration Against Open Source}

\subsection{1. Attacks on Transgender Developers}
\textbf{Crimes:}
\begin{itemize}
    \item Banned transgender individuals from the military, cutting funding for trans developers in defense-related open-source projects.
    \item Removed workplace protections for trans employees.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support open-source projects led by marginalized communities.
\end{itemize}

\subsection{2. Net Neutrality Repeal}
\textbf{Crimes:}
\begin{itemize}
    \item FCC, under Ajit Pai, removed net neutrality protections.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Advocate for net neutrality legislation.
\end{itemize}

\subsection{3. Favoring Corporate Interests Over Open-Source}
\textbf{Crimes:}
\begin{itemize}
    \item Strengthened DMCA protections for corporations.
\end{itemize}

\textbf{Countermeasures:}
\begin{itemize}
    \item Support legal defense funds for open-source developers.
\end{itemize}

\section{Conclusion}
Corporations and governments exploit open-source software while suppressing user freedoms, violating licenses, and using legal threats against developers. The open-source community must take action through boycotts, legal challenges, and public pressure campaigns.

\end{document}
